Software Defect Prediction: Review, Commentary, and Future Work

### 2015-12-14 paper/paper.tex
Some minor additions and typo fixes

\numberofauthors{3} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Matthew Neal\\
       \affaddr{Department of Computer Science}\\
       \affaddr{North Carolina State University}\\
       \affaddr{Raleigh, North Carolina, USA}\\
       \email{meneal@ncsu.edu}
% 2nd. author
\alignauthor
Joseph Sankar\\
	   \affaddr{Department of Computer Science}\\
       \affaddr{North Carolina State University}\\
       \affaddr{Raleigh, North Carolina, USA}\\
       \email{jesankar@ncsu.edu}
% 3rd. author
\alignauthor Alexandar Sobran\\
       \affaddr{Department of Computer Science}\\
       \affaddr{North Carolina State University}\\
       \affaddr{Raleigh, North Carolina, USA}\\
       \email{aisobran@ncsu.edu}
\and  % use '\and' if you need 'another row' of author names
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

@@

Arisholm et al \cite{Arisholm} examined different ways to build and evaluate fault prediction models. First, they tested a variety of modeling techniques, such as neural networks, C4.5 with some variants, support vector machines, and logistic regression. They then looked at different metrics:  Process measures, OO code measures, and delta measures. Finally, they looked at ROC area and cost-effectiveness as evaluation criteria. They found that the choice of modeling technique did not have much of an impact when evaluated with both criteria tested. Among the metric sets, they found that process measures provide a significant improvement over the others, even though they are typically more costly to collect.  They also suggested cost-effectiveness as a good evaluation technique instead of traditional techniques like precision and recall as smarter decisions can be made to prioritize which parts of the project are tested and bug-fixed.

@@

Traditional software fault prediction models are trained on historical project data. Since new projects do not have such a volume of historical data, these fault prediction models are not as effective at within-project defect prediction. A possible solution to this issue is cross-project prediction which uses data from one project to predict defects in another. Still, models using this technique exhibit poor performance. Rahman et al \cite{Rahman} argued that one reason for such behavior is that standard evaluation measures such as precision, recall, and F-measure are taken at specific threshold settings, while they really should be taken in a range of time/cost vs. quality tradeoffs. They took the standard measures at a variety of tradeoffs and found that cross-project defect prediction is at least as good as within-project defect prediction, and sometimes substantially better.

@@

One major possibility for using NASA datasets is that most of their software is critical. A malfunction or crash due to a software defect is not only costly, but can also be deadly. NASA's software needs to be thoroughly tested and bug-fixed before it is ready for use. NASA's datasets contain code metrics and defect information, which is easy to mine and create training and test data from.

NASA datasets are also publicly available. Researchers can more easily verify the results obtained in a study. Also, since these datasets are static, they can be used as a baseline to compare the results from a newly created model against those from other studies.
\subsection{Windows Vista}

>>>>

\numberofauthors{3} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Matthew Neal\\
       \affaddr{Department of Computer Science}\\
       \affaddr{North Carolina State University}\\
       \affaddr{Raleigh, North Carolina, USA}\\
       \email{meneal@ncsu.edu}
% 2nd. author
\alignauthor
Joseph Sankar\\
	   \affaddr{Department of Computer Science}\\
       \affaddr{North Carolina State University}\\
       \affaddr{Raleigh, North Carolina, USA}\\
       \email{jesankar@ncsu.edu}
% 3rd. author
\alignauthor Alexander Sobran\\
       \affaddr{Department of Computer Science}\\
       \affaddr{North Carolina State University}\\
       \affaddr{Raleigh, North Carolina, USA}\\
       \email{aisobran@ncsu.edu}
\and  % use '\and' if you need 'another row' of author names
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

@@

Arisholm et al \cite{Arisholm} examined different ways to build and evaluate fault prediction models. First, they tested a variety of modeling techniques, such as neural networks, C4.5 with some variants, support vector machines, and logistic regression. They then looked at different metrics:  Process measures, object oriented code measures, and delta measures. Finally, they looked at ROC area and cost-effectiveness as evaluation criteria. They found that the choice of modeling technique did not have much of an impact when evaluated with both criteria tested. Among the metric sets, they found that process measures provide a significant improvement over the others, even though they are typically more costly to collect.  They also suggested cost-effectiveness as a good evaluation technique instead of traditional techniques like precision and recall as smarter decisions can be made to prioritize which parts of the project are tested and bug-fixed.

@@

Traditional software fault prediction models are trained on historical project data. Since new projects do not have such a volume of historical data, these fault prediction models are not as effective at within-project defect prediction. A possible solution to this issue is cross-project prediction which uses data from one project to predict defects in another. Still, models using this technique exhibit poor performance. Rahman et al \cite{Rahman} argued that one reason for such behavior is that standard evaluation measures such as precision, recall, and F-measure are taken at specific threshold settings, while they really should be taken in a range of time/cost vs. quality trade offs. They took the standard measures at a variety of tradeoffs and found that cross-project defect prediction is at least as good as within-project defect prediction, and sometimes substantially better.

@@

One major reason for using NASA datasets is that most of their software is critical. A malfunction or crash due to a software defect is not only costly, but can also be deadly. NASA's software needs to be thoroughly tested and bug-fixed before it is ready for use. Software defect models which work well on these datasets can be claimed to be more reliable and trustworthy. Additionally, NASA's datasets contain code metrics and defect information, which is easy to mine and create training and test data from.

NASA datasets are publicly available. Researchers can more easily verify the results obtained in a study. Also, since these datasets are static, they can be used as a baseline to compare the results from a newly created model against those from other studies.
\subsection{Windows Vista}
